MSDS6371Project

### 2020-11-22 MSDS6371Project.Rmd
updates

#Move forward with next batch of exploration
amesHouse %>% dplyr::select(lSalePrice,BsmtFullBath,BsmtHalfBath,HalfBath,BedroomAbvGr,KitchenAbvGr,
                     TotRmsAbvGrd)%>%
  ggpairs()

#The only variable seem to have good correlation with lSalePrice is FullBath,TotRmsAbvGrd.
#???If we should change BsmtFullBath,BsmtHalfBath,HalfBath,BedroomAbvGr,KitchenAbvGr to factors???
#Keep going
amesHouse %>% dplyr::select(lSalePrice,GarageYrBlt,GarageCars,GarageArea) %>% ggpairs()
#The above variables all seem to have a good linear correlation with lSalePrice
#Keep going
amesHouse %>% dplyr::select(lSalePrice,WoodDeckSF,OpenPorchSF,EnclosedPorch,X3SsnPorch,ScreenPorch,MiscVal)%>%
  ggpairs()
#linear relationships don't seem particularly strong except WoodDeckSF, OpenPorchSF

@@

#write a program to pretict 100 different combination to test forward selection model
iterations = 100
splitPerc = 0.8
total_RMSE = 0
for(i in 1:iterations){
  trainIndices = sample(1:dim(variables.used)[1],round(splitPerc * dim(variables.used)[1]))
  train = variables.used[trainIndices,]
  test = variables.used[-trainIndices,]
  forward_fit = lm(lSalePrice~.-Id,data=train)
  forward.model = ols_step_forward_aic(forward_fit,penter=0.15)
  prediction = predict(forward.model$model,test)
  squared_MSPE = mean((test$lSalePrice - prediction)^2)
  temp_RMSE = sqrt(squared_MSPE)
  total_RMSE = total_RMSE+temp_RMSE
}
#CV Press=1.003755
exp(total_RMSE/iterations)
#Build model with full dataset for fitting
forward_fit = lm(lSalePrice~.-Id,data=variables.used)
forward.model = ols_step_forward_aic(forward_fit,penter=0.15)
forward.model$model
forward.model
ols_plot_resid_stand(forward.model$model)
ols_plot_cooksd_bar(forward.model$model)
plot(forward.model$model)

@@

@@

testVariable$lSalePriceBackward = predict(backward.model$model,testVariable)
testVariable$SalePrice = exp(testVariable$lSalePriceBackward)
result.backward = testVariable %>% dplyr::select(Id,SalePrice)
write.csv(result.backward,"Backward_Prediction_Miller_YU.csv",row.names = FALSE)
```

>>>>

#Move forward with next batch of exploration
amesHouse %>% dplyr::select(SalePrice,BsmtFullBath,BsmtHalfBath,HalfBath,BedroomAbvGr,KitchenAbvGr,
                     TotRmsAbvGrd)%>%
  ggpairs()
amesHouse %>% dplyr::select(lSalePrice,BsmtFullBath,BsmtHalfBath,HalfBath,BedroomAbvGr,KitchenAbvGr,
                     TotRmsAbvGrd)%>%
  ggpairs()

#The only variable seem to have good correlation with lSalePrice is FullBath,TotRmsAbvGrd.
#???If we should change BsmtFullBath,BsmtHalfBath,HalfBath,BedroomAbvGr,KitchenAbvGr to factors???
#Keep going
amesHouse %>% dplyr::select(SalePrice,GarageYrBlt,GarageCars,GarageArea) %>% ggpairs()
amesHouse %>% dplyr::select(lSalePrice,GarageYrBlt,GarageCars,GarageArea) %>% ggpairs()
#The above variables all seem to have a good linear correlation with lSalePrice
#Keep going
amesHouse %>% dplyr::select(SalePrice,WoodDeckSF,OpenPorchSF,EnclosedPorch,X3SsnPorch,ScreenPorch,MiscVal)%>%
  ggpairs()
amesHouse %>% dplyr::select(lSalePrice,WoodDeckSF,OpenPorchSF,EnclosedPorch,X3SsnPorch,ScreenPorch,MiscVal)%>%
  ggpairs()
#linear relationships don't seem particularly strong except WoodDeckSF, OpenPorchSF
#Overall, lSalePrice seem to improve the correlation with our important predictors a bit. So we will proceed
#with lSalePrice Analysis

@@

#write a program to pretict 100 different combination to test forward selection model
iterations = 100
splitPerc = 0.8
total_RMSE = 0
for(i in 1:iterations){
  trainIndices = sample(1:dim(variables.used)[1],round(splitPerc * dim(variables.used)[1]))
  train = variables.used[trainIndices,]
  test = variables.used[-trainIndices,]
  forward_fit = lm(lSalePrice~.-Id,data=train)
  forward.model = ols_step_forward_aic(forward_fit,penter=0.15)
  prediction = predict(forward.model$model,test)
  squared_MSPE = mean((test$lSalePrice - prediction)^2)
  temp_RMSE = sqrt(squared_MSPE)
  total_RMSE = total_RMSE+temp_RMSE
}
#total RMSE = 0.00374748... RMSE = 839.29 under original SalePrice scale
total_RMSE/iterations
#CV Press=1.003755
exp(total_RMSE/iterations)
#Build model with full dataset for fitting
forward_fit = lm(lSalePrice~.-Id,data=variables.used)
forward.model = ols_step_forward_aic(forward_fit,penter=0.15)
forward.model$model
forward.model
ols_plot_resid_stand(forward.model$model)
ols_plot_cooksd_bar(forward.model$model)
plot(forward.model$model)

@@

#Try Mass Library Forward model
forward.model2 = stepAIC(forward_fit,direction="forward")
forward.model2$model

@@

testVariable$lSalePriceBackward = predict(backward.model$model,testVariable)
testVariable$SalePrice = exp(testVariable$lSalePriceBackward)
result.backward = testVariable %>% dplyr::select(Id,SalePrice)
write.csv(result.backward,"Backward_Prediction_Miller_YU.csv",row.names = FALSE)

#Try Mass Library Forward model - Same result 0.15432
backward.model2 = stepAIC(backward_fit,direction="backward")
backward.model2

#Testing with Mass Library
testVariable$lSalePriceBackward = predict(backward.model2,testVariable)
testVariable$SalePrice = exp(testVariable$lSalePriceBackward)
result.backward = testVariable %>% dplyr::select(Id,SalePrice)
write.csv(result.backward,"Backward_Prediction_2_Miller_YU.csv",row.names = FALSE)
```
